Matching Bullets

### 2015-12-10 imaging-paper.Rnw
Correct some small typos

-%\hh{XXX add parameter estimates? $\hat{r} \approx 4500$ - indicating a 9 mm bullet, amount of degrees covered by land?  }

\begin{figure}[hbtp]
\begin{subfigure}[t]{\linewidth}
\caption{\label{fig:residuala}Residual structure of a surface crosscut at $x = 1.5625$ (bottom of the bullet).}
<<residual2, dependson='fixedX', echo=FALSE, warning=FALSE, fig.height=3, out.width='\\linewidth'>>=
qplot(data=subset(dbr111, x <= 1.5625), y, value-ypred, #colour=factor(x),
      geom="line", size=I(1)) +
#  scale_colour_brewer("x", palette="Paired") + 
  theme_bw() + 
  geom_hline(yintercept = 0, colour="grey50") +
  ylab(expression(paste("Residuals (in ",mu,"m)", sep=""))) + 
  theme(legend.position="bottom")
@
\end{subfigure}    
\begin{subfigure}[t]{\linewidth}
\caption{\label{fig:residualb} Residual structure of a surface crosscut at $x = 100.00$}
<<residual, dependson='fixedX', echo=FALSE, warning=FALSE, fig.height=3, out.width='\\linewidth'>>=
#qplot(data=subset(dbr111, x <= 80*1.5625^2 & x >=75*1.5625^2), y, value-ypred,
qplot(data=subset(dbr111, x == 100), y, value-ypred,  #colour=factor(x), 
      geom="line", size=I(1)) +
#  scale_colour_brewer("x", palette="Paired") + 
  geom_hline(yintercept = 0, colour="grey50") +
  theme_bw() + 
  ylab(expression(paste("Residuals (in ",mu,"m)", sep=""))) + 
  theme(legend.position="bottom")
@
\end{subfigure}
\caption{\label{fig:residual} Residual structure of  circular fits at two different cross-section. Both residual plots show systematic structures, indicating that a circular fit is not entirely appropriate. }
\end{figure}

A single cylinder as a fit is unlikely to be a particularly good fit, because  there seem to be quite massive deformations in vertical direction. Even when we fit a circle to each cross section of the bullet, as in Figure~\ref{fig:circlefits}, we can not address all of these issues. While the wider circumference at the base of the bullet can be resolved by individual circular fits, the systematic residual structure in Figure~\ref{fig:residualb} stays the same.

@@

\begin{figure}[hbtp]
  \centering
<<circlefits, echo=FALSE, fig.width=7, fig.height=7, out.width='\\linewidth', warning=FALSE>>=
qplot(y, resid, data=subset(db2, x == 100), #colour=factor(x), 
      geom="line", size=I(.75), colour=I("grey70")) + 
  facet_wrap(~part, ncol=2) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(aes(y, resid, group = x), colour="black", size=.75, alpha=0.5,
             data = filter(db1, part==5, x == 100)[,c("y", "resid", "x")]) +
  ylab("Residuals from circular fit") +
  ggtitle("Bullet 1-5 in black")
@
\caption{Circle fit for each cross section of bullet 2, with bullet 1-5 overlaid.\label{fig:circlefits} Bullet 1-5 matches best with the bullet 2-1}
\end{figure}

>>>>

%\hh{XXX add parameter estimates? $\hat{r} \approx 4500$ - indicating a 9 mm bullet, amount of degrees covered by land?  }

\begin{figure}[hbtp]
\begin{subfigure}[t]{\linewidth}
\caption{\label{fig:residuala}Residual structure of a surface crosscut at $x = 1.5625$ (bottom of the bullet).}
<<residual2, dependson='fixedX', echo=FALSE, warning=FALSE, fig.height=3, out.width='\\linewidth'>>=
qplot(data=subset(dbr111, x <= 1.5625), y, value-ypred, #colour=factor(x),
      geom="line", size=I(1)) +
#  scale_colour_brewer("x", palette="Paired") + 
  theme_bw() + 
  geom_hline(yintercept = 0, colour="grey50") +
  ylab(expression(paste("Residuals (in ",mu,"m)", sep=""))) + 
  theme(legend.position="bottom")
@
\end{subfigure}    
\begin{subfigure}[t]{\linewidth}
\caption{\label{fig:residualb} Residual structure of a surface crosscut at $x = 100.00$}
<<residual, dependson='fixedX', echo=FALSE, warning=FALSE, fig.height=3, out.width='\\linewidth'>>=
#qplot(data=subset(dbr111, x <= 80*1.5625^2 & x >=75*1.5625^2), y, value-ypred,
qplot(data=subset(dbr111, x == 100), y, value-ypred,  #colour=factor(x), 
      geom="line", size=I(1)) +
#  scale_colour_brewer("x", palette="Paired") + 
  geom_hline(yintercept = 0, colour="grey50") +
  theme_bw() + 
  ylab(expression(paste("Residuals (in ",mu,"m)", sep=""))) + 
  theme(legend.position="bottom")
@
\end{subfigure}
\caption{\label{fig:residual} Residual structure of circular fits at two different cross-section. Both residual plots show systematic structures, indicating that a circular fit is not entirely appropriate.}
\end{figure}

A single cylinder as a fit is unlikely to be a particularly good fit, because there seem to be quite massive deformations in the vertical direction. Even when we fit a circle to each cross section of the bullet, as in Figure~\ref{fig:circlefits}, we can not address all of these issues. While the wider circumference at the base of the bullet can be resolved by individual circular fits, the systematic residual structure in Figure~\ref{fig:residualb} stays the same.

@@

\begin{figure}[hbtp]
  \centering
<<circlefits, echo=FALSE, fig.width=7, fig.height=7, out.width='\\linewidth', warning=FALSE>>=
qplot(y, resid, data=subset(db2, x == 100), #colour=factor(x), 
      geom="line", size=I(.75), colour=I("grey70")) + 
  facet_wrap(~part, ncol=2) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(aes(y, resid, group = x), colour="black", size=.75, alpha=0.5,
             data = filter(db1, part==5, x == 100)[,c("y", "resid", "x")]) +
  ylab("Residuals from circular fit") +
  ggtitle("Bullet 1-5 in black")
@
\caption{Circle fit for each cross section of bullet 2, with bullet 1-5 overlaid.\label{fig:circlefits} Bullet 1-5 matches best with the bullet 2-1.}
\end{figure}
